Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
Some stats about errors

\todo{What are the means and variance of different variables?}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=\columnwidth]{how_many_precise.pdf}
  \caption{Participant data for quesstion type 1 plotted by measured and expected bias.}
  \label{figure_q1}
\end{figure}

@@

We had no way of ensuring that participants did not take screenshots in order to answer later questions about the precise visualizations.
\todo{some more detail here, now that we collected data}

>>>>

In this study we wanted to understand whether analysts have a bias in how they recall precise data.
Before we analyze the bias between what participants remembered from the approximate and precise visualizations, we look at the relative errors (absolute bias) independently.
We removed outliers where the relative bias was larger than 4 times the standard deviation using sigma clipping.
Table \ref{table_errors} summarized the results.
Since we expect a bias (R1), the errors in the precise visualization should be larger.
The errors for the type 1 questions were significantly larger ($p=0.0002$ for type 1), while we could not see a significant effect of type 2 questions.  \todo{What's happening?}

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The errors (absolute values of the bias) for different questions}
\label{table_errors}
\centering
\begin{tabular}{|l||r|r|r|r|}
\hline
Question & Data        & Mean error & Standard deviation \\ \hline
\hline
type 1   & approx      & 2.18\%     & 3.52\%             \\ \hline
type 1   & precise     & 8.67\%     & 13.05\%            \\ \hline
type 2   & approx      & 41.99\%    & 52.84\%            \\ \hline
type 2   & precise     & 46.87\%    & 45.36\%            \\ \hline
\end{tabular}
\end{table}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=\columnwidth]{how_many_precise.pdf}
  \caption{Participant data for question type 1 plotted by measured and expected bias.}
  \label{figure_q1}
\end{figure}

@@

We had no way of ensuring that participants did not take screenshots or notes in order to answer later questions about the precise visualizations.
\todo{some more detail here, now that we collected data}
